Q.1. Multiple of 3 or 5
   If we list all the natural numbers below 10 that are multiples of 3 or 5, we get 3, 5, 6 and 9. The sum of these multiples is 23.Find the sum of all the multiples of 3 or 5 below 1000.


[b]A Constant Time Approach[/b]

This is a mathematical solution with a time complexity of O(1). I used the basic formula for the addition of natural numbers and modified it a little bit for our specific situation.

[g][b]Approach:[/b][/g]
We can find the sum of the multiples of a number as follows:
$$
\begin{aligned}
&= (x\times1) + (x\times2) + (x\times3) + \cdots + (x\times n) \\
&= x\times(1+2+3+\cdots+n) \\
&= x\times\frac{n(n+1)}{2} \\
&= x\times\frac{n^2+n}{2}
\end{aligned}
$$

Using this formula, we can calculate the sum of the multiples of 3 and the multiples of 5, and then add them together. 

However, there is a catch. We only want to add the common multiples of 3 and 5 once. Because we calculated them separately, these common multiples are counted two times in our current total. 

To fix this, we need to subtract the common multiples that were added twice. Since the common multiples of 3 and 5 happen to be the multiples of 15, we calculate the sum of the multiples of 15 and subtract it from our final answer. This gives us the desired output.

Finally, regarding the 999/3 part in the program: this calculates the maximum natural number that can be multiplied by 3 without generating a number of 1000 or greater. The exact same process is repeated for 5 and 15.

[g]C++ Implementation:[/g]
[code=cpp]
#include <iostream>
using namespace std;

int main()
{
    int n = 999/3;
    int m = 999/5;
    int p = 999/15;    // for common multiples

    int sum_mltpl_3 = 3 * ((n*n + n)/2);
    int sum_mltpl_5 = 5 * ((m*m + m)/2);
    int sum_mltpl_15 = 15 * ((p*p + p)/2);

    int result = sum_mltpl_3 + sum_mltpl_5 - sum_mltpl_15;

    cout << "The sum is: " << result <<endl;
    return 0;
}
[/code]